Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-09-27 ms/ms.Rmd
ms: skrim GPR data including new wave speed calibration

GPR data.

>>>>

Besides the depth and occurrence measurements described above, we also measured peat depth in three subjectively-chosen, individual mires, using ground-penetrating radar (GPR).
We used the Malå ProEx GPR system (Guideline Geo AB, Sweden) with its \unit{500\,MHz} shielded antenna mounted in a plastic sledge, and its control unit connected to a GNSS receiver.
At each of the three mires we recorded GPR traces along walking transects that covered the extent of the mire, mostly in traversing, zigzag patterns with between \unit{5\,m} and \unit{20\,m} spacing at their vertices.
Along the GPR transects we also probed peat depth at marked trace locations, to be able to calibrate the GPR wave speed velocity.
We processed the GPR data with Reflex2DQuick software (v.3.0; Sandmeier Scientific Software, Germany), applying a time-zero correction, a dewow filter, and a gain filter based on observed energy decay.
Then we picked strong reflectors in the radargrams that we interpreted as the base of the peat column.
We used picks at marked trace locations to calibrate wave speed velocity; we pooled calibration points across the three mires and fitted a linear regression of depth on one-way travel time with the intercept fixed at zero.
In total we had 46 calibration points along \unit{3.5\,km} of GPR transects.
Finally, we used the calculated wave velocity (\unit{0.0387\,m\,ns^{-1}}, $R^2 = 0.874$) to convert the travel times of all picks to calibrated peat depths.

### 2024-09-27 ms/ms.tex
ms: skrim GPR data including new wave speed calibration

GPR data.

>>>>

Besides the depth and occurrence measurements described above, we also measured peat depth in three subjectively-chosen, individual mires, using ground-penetrating radar (GPR).
We used the Malå ProEx GPR system (Guideline Geo AB, Sweden) with its \unit{500\,MHz} shielded antenna mounted in a plastic sledge, and its control unit connected to a GNSS receiver.
At each of the three mires we recorded GPR traces along walking transects that covered the extent of the mire, mostly in traversing, zigzag patterns with between \unit{5\,m} and \unit{20\,m} spacing at their vertices.
Along the GPR transects we also probed peat depth at marked trace locations, to be able to calibrate the GPR wave speed velocity.
We processed the GPR data with Reflex2DQuick software (v.3.0; Sandmeier Scientific Software, Germany), applying a time-zero correction, a dewow filter, and a gain filter based on observed energy decay.
Then we picked strong reflectors in the radargrams that we interpreted as the base of the peat column.
We used picks at marked trace locations to calibrate wave speed velocity; we pooled calibration points across the three mires and fitted a linear regression of depth on one-way travel time with the intercept fixed at zero.
In total we had 46 calibration points along \unit{3.5\,km} of GPR transects.
Finally, we used the calculated wave velocity (\unit{0.0387\,m\,ns^{-1}}, \(R^2 = 0.874\)) to convert the travel times of all picks to calibrated peat depths.
